### 2018-11-14 Sections/cloud_quantum_computing.tex
Parallelisation of dist grover

>>>>

% Distributed quantum search algorithm

\subsubsection{Distributed quantum search algorithm}\index{Distributed quantum search algorithm}

The Grover quantum search algorithm (Sec.~\ref{sec:quantum_search}) can be easily parallelised\index{Parallelisation} by partitioning the search space\index{Search space!Partitioning}, and allocating a different partition to each node.

Suppose we wish to search over the $N$-bit space $x$, to find a satisfying solution to some oracle function \mbox{$f(x)=1$}. Let there be $M$ nodes available for computation, where for simplicity we assume $M$ is a power of 2. We designate each of the nodes a $\log_2 M$-bit identification number\index{Identification numbers},
\begin{align}
	y=[0,M-1].
\end{align}
We now program each node to search over a smaller search space $x'$, which is \mbox{$N-\log_2 M$} bits in length, concatenated with the node's identification number to produce the full range of $x$. The input to each oracle is now,
\begin{align}
x = x'\frown y,
\end{align}
where `$\frown$' denotes string concatenation.

For example, with four nodes the 2-bit identification numbers are, 
\begin{align}
	y=\{00,01,10,11\}.
\end{align}
If the input search space is $N$-bits in length, then each of the nodes are assigned the search-space \mbox{$x'\frown y$}, where $x'$ is a \mbox{$N-2$}-bit number.

It can easily be seen that this approach is compatible with the quantum \textsc{MapReduce} formalism, where the \textsc{Map} function assigns the partitions denoted by identification numbers $y$, and the \textsc{Reduce} function collects satisfying arguments.

The net computational speedup is linear, simply a factor equal to the number of nodes, $M$. Note that this approach does not exploit entanglement between nodes, and does not offer a `quantum' (i.e super-linear) speedup, since it is really just brute-force partitioning of a problem into smaller more efficient ones that are attacked independently, much like classical parallelisation.

% Distributed unitary error averaging

### 2018-11-14 Sections/essay_to_the_future_QKD.tex
Parallelisation of dist grover

The second is to use free-space\index{Free-space} quantum communication techniques via satellite links. Satellite QKD is achievable with present-day technology. Here satellites are used as intermediate trusted nodes\index{Trusted nodes} for communication between locations on the ground. Direct links can be established between ground stations and the satellite, thus enabling communication between parties separated by long distances, potentially relaying across a satellite constellation network to overcome line-of-sight limitations from the Earth's curvature\index{Line-of-sight}\index{Earth curvature}. Satellite QKD suffers comparatively very low loss between satellites in orbit, but the satellite-to-ground links\index{Satellite-to-ground links}, which cannot be avoided at the endpoints, suffer around 40dB loss when propagating through the effective atmospheric thickness\index{Effective atmospheric thickness} of $\sim$10km when the satellite is directly overhead (and worse for satellites with lower azimuth). The atmospheric loss is a major hurdle, since distribution of a Bell pair between two ground stations effectively incurs 80dB inefficiency, meaning that only 1 in every 100,000,000 Bell pairs are successfully distributed \latinquote{Stupor}. Nonetheless, in China, satellite QKD over 1200km has been demonstrated \cite{bib:liao2017satellite}, sufficient for sharing a secret-key\index{Secret-keys} for private-key cryptography\index{Private-key!Cryptography} with guaranteed key secrecy.

>>>>

The second is to use free-space\index{Free-space} quantum communication techniques via satellite links. Satellite QKD is achievable with present-day technology. Here satellites are used as intermediate trusted nodes\index{Trusted nodes} for communication between locations on the ground. Direct links can be established between ground stations and the satellite, thus enabling communication between parties separated by long distances, potentially relaying across a satellite constellation network to overcome line-of-sight limitations from the Earth's curvature\index{Line-of-sight}\index{Earth curvature}. Satellite QKD suffers comparatively very low loss between satellites in orbit, but the satellite-to-ground links\index{Satellite-to-ground links}, which cannot be avoided at the endpoints, suffer around 40dB loss when propagating through the effective atmospheric thickness\index{Effective atmospheric thickness} of $\sim$10km when the satellite is directly overhead (and worse for satellites with lower azimuth). The atmospheric loss is a major hurdle, since distribution of a Bell pair between two ground stations effectively incurs 80dB inefficiency, meaning that only 1 in every 100,000,000 Bell pairs are successfully distributed \latinquote{Stupor}. Nonetheless, in China, satellite QKD over 1200km has been demonstrated \cite{bib:liao2017satellite}, sufficient for sharing a secret-key\index{Private-keys} for private-key cryptography\index{Private-key!Cryptography} with guaranteed key secrecy.
